---
title: "Tracking the evolution of the pandemic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tracking the evolution of the pandemic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Data description
This packages contain a dashboard shows recent development of the COVID19 pandemic. ]

This package contain 2 dataset: `data_total` and `data_total_newdaily`. The data is downloaded from [Johns HopkinsCSSE](https://github.com/CSSEGISandData/COVID-19a). Both datasets contain the information about the spreading of the COVID19 pandemic. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.5
)
```

```{r setup}
library(icecovid19)
library(tibble)
library(ggplot2)
library(dplyr)

```

### data_total dataset

data_total is a dataset contains the number of COVID19 cases worldwide from 22/01/2020 to 06/10/2020, along with the latitude and longitude of the region in which cases were recorded.  
There are 3 type of cases: Confirmed, deceased and recoveredIt can be accessed via 
```{r}
library(icecovid19)
as_tibble(data_total)
```

#### Exploration of the data

Evolution of the pandemic in Australia

```{r}
data_total %>% filter(`Country/Region` == "Australia") %>%
  ggplot(aes(x = date, y = confirmed))+
  geom_line(color = "steelblue", alpha = 0.7, size = 2)+
  ggtitle("Evolution of COVID19 in Australia")+
  xlab("Date")+
  ylab("Confirmed cases (person)")+
  theme_bw()
```

### data_total_newdaily
Data for new cases of COVID19 from 22/01/2020 to 06/10/2020
 
A dataset contains the number of COVID19 cases worldwide from 22/01/2020 to 06/10/2020. Data is in longer format, with variable var contains 6 types of cases: Confirmed, deceased, recovered, new daily confirmed, new daily death and new daily recovered.


#### Exploration of the data
```{r}
data_total_newdaily %>% filter(`Country/Region` == "Australia") %>%
  ggplot(aes(x = date, y = value, color = var))+
  geom_line()+
  ggtitle("Evolution of COVID19 in Australia")+
  xlab("Date")+
  ylab("Confirmed cases (person)")+
  theme_bw()
```
